Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-01-18 2017-Xudong-SMT/FM-2018-extended.tex
Modify the TMAX.
TMAX from IntLiteral to Variable.
Then the transitions changed.

\begin{figure}[h]
\begin{mathpar}
    \openrule{\{s1 \xrightarrow{\OTvar{fail(false)}} s1, t1 \xrightarrow{\OTvar{resume(true)}} t0\}, ~~\{\xrightarrow{hb}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
    \OTland \OTvar{resume(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland \OTvar{hb}=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\OTland \OTvar{v}=\OTvar{\underline{fail}}\OTland \OTvar{b}_1=\OTvar{b}_2\\
    \OTland \OTvar{(}\OTvar{b}_1\lor\OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
    	   {\ostate{s1,t1} \xrightarrow{\OTvar{v}} \ostate{s1,t0}}\\
  \end{mathpar}
\caption{One of the unsatisfiable open transitions in FailureTimer}  \label{schema:unsat-ot}
\end{figure}

@@

\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, frame=single]
   {s0---fail(true)-->s1, t0---start(true)-->t1}, {---:hb_B:13:1-->},
   (fail(true)=fail(b1:sva_SV0:1:1))/\(start(true)=start(b2:sva_SV0:1:1))
   /\(:hb_B:13:1=fail(b0:sva_SV0:1:1))/\((b1:sva_SV0:1:1=b2:sva_SV0:1:1)
   /\(~(b1:sva_SV0:1:1\/b2:sva_SV0:1:1)\/b0:sva_SV0:1:1))/\(_fail_=:ra:1:1),
   {t := 4}
OT ------------------------------------------------------------
        <s0_t0>-----:ra:1:1----><s1_t1>

   {s0---resume(false)-->s0, t0---resume(false)-->t0},   {---:hb_B:16:2-->},
   (resume(false)=resume(b1:sva_SV1:1:2))/\(resume(false)=resume(b2:sva_SV1:1:2))
   /\(:hb_B:16:2=resume(b0:sva_SV1:1:2))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2)
   /\(~(b1:sva_SV1:1:2\/b2:sva_SV1:1:2)\/b0:sva_SV1:1:2))/\(_resume_=:ra:1:2), {}
OT ------------------------------------------------------------
        <s0_t0>-----:ra:1:2----><s0_t0>

   {},   {---:hb_B:118:6-->},   (:hb_B:118:6=finish)/\(finish=:ra:1:6),  {}
OT ------------------------------------------------------------
        <s0_t0>-----:ra:1:6----><s0_t0>

   {s1---fail(false)-->s1, t1---start(false)-->t1},   {---:hb_B:13:1-->},
   (fail(false)=fail(b1:sva_SV0:1:1))/\(start(false)=start(b2:sva_SV0:1:1))
   /\(:hb_B:13:1=fail(b0:sva_SV0:1:1))/\((b1:sva_SV0:1:1=b2:sva_SV0:1:1)
   /\(~(b1:sva_SV0:1:1\/b2:sva_SV0:1:1)\/b0:sva_SV0:1:1))/\(_fail_=:ra:1:1), {}
OT ------------------------------------------------------------
        <s1_t1>-----:ra:1:1----><s1_t1>

   {s1---resume(true)-->s0, t1---resume(true)-->t0},   {---:hb_B:16:2-->},
   (resume(true)=resume(b1:sva_SV1:1:2))/\(resume(true)=resume(b2:sva_SV1:1:2))
   /\(:hb_B:16:2=resume(b0:sva_SV1:1:2))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2)
   /\(~(b1:sva_SV1:1:2\/b2:sva_SV1:1:2)\/b0:sva_SV1:1:2))/\(_resume_=:ra:1:2), {}
OT ------------------------------------------------------------
        <s1_t1>-----:ra:1:2----><s0_t0>

   {t1---tick-->t1},   {},   (t!=0)/\(_tick_=:ra:1:3),   {t := (t-1)}
OT ------------------------------------------------------------
        <s1_t1>-----:ra:1:3----><s1_t1>

   {},  {---:hb_B:118:6-->},  (:hb_B:118:6=finish)/\(finish=:ra:1:6),  {}
OT ------------------------------------------------------------
        <s1_t1>-----:ra:1:6----><s1_t1>

   {s1---timeout-->s2, t1---timeout-->t0},  {},  (t=0)/\(ask=:ra:1:4),  {}
OT ------------------------------------------------------------
        <s1_t1>-----:ra:1:4----><s2_t0>

   {s2---resume(false)-->s2, t0---resume(false)-->t0},   {---:hb_B:16:2-->},
   (resume(false)=resume(b1:sva_SV1:1:2))/\(resume(false)=resume(b2:sva_SV1:1:2))
   /\(:hb_B:16:2=resume(b0:sva_SV1:1:2))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2)
   /\(~(b1:sva_SV1:1:2\/b2:sva_SV1:1:2)\/b0:sva_SV1:1:2))/\(_resume_=:ra:1:2),
   {}
OT ------------------------------------------------------------
        <s2_t0>-----:ra:1:2----><s2_t0>

   {s2---reset-->s0},   {},   (reset=:ra:1:5),   {}
OT ----------------------------------------------------------
        <s2_t0>-----:ra:1:5----><s0_t0>

   {},  {---:hb_B:118:6-->},  (:hb_B:118:6=finish)/\(finish=:ra:1:6),  {}
OT ------------------------------------------------------------
        <s2_t0>-----:ra:1:6----><s2_t0>
\end{lstlisting}

\begin{figure}[h]  
$\begin{array}{r@{}l}
    ot_1  = &\openrule{\{s0 \xrightarrow{\OTvar{fail(true)}} s1, t0 \xrightarrow{\OTvar{start(true)}} t1\}, ~~\{\xrightarrow{hb_1}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
    \OTland \OTvar{start(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland hb_1=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\OTland v_1=\OTvar{\underline{fail}}\OTland \OTvar{b}_1 = \OTvar{b}_2
    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
    	   {\ostate{s0,t0} \xrightarrow{v_1} \ostate{s1,t1}}\\
\end{array}$

$\begin{array}{r@{}l}
    ot_2  = &\openrule{\{s0 \xrightarrow{\OTvar{resume(false)}} s0, t0 \xrightarrow{\OTvar{resume(false)}} t0\}, ~~\{\xrightarrow{hb_2}\},~~\OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_1\OTvar{)}\\
    \OTland \OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_2=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\OTland v_2=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{t := 4\}}
    	    {\ostate{s0,t0} \xrightarrow{v_2} \ostate{s0,t0}}\\
\end{array}$

@@

$\begin{array}{r@{}l}
    ot_6  = &\openrule{\{t1 \xrightarrow{\OTvar{tick}} t1\}, ~~\{\},~~t\neq 0\OTland v_6=\OTvar{\underline{tick}}, ~~\{t := t-1 \}}
    	   {\ostate{s1,t1} \xrightarrow{v_6} \ostate{s1,t0}}\\
\end{array}$

>>>>

\begin{figure}[h]
\begin{mathpar}
    ot = \openrule{\{s1 \xrightarrow{fail(false)} s1, t1 \xrightarrow{resume(true)} t0\}, ~~\{\xrightarrow{hb}\},~~fail(false)=fail(b_1)\\
    \OTland resume(true)=start(b_2)\OTland hb=fail(b_0)\OTland v=\underline{fail}\OTland b_1=b_2\\
    \OTland (b_1\lor b_2) \Rightarrow b_0, ~~\{\}}
    	   {\ostate{s1,t1} \xrightarrow{v} \ostate{s1,t0}}\\
  \end{mathpar}
\caption{One of the unsatisfiable open transitions in FailureTimer}  \label{schema:unsat-ot}
\end{figure}

@@

\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, frame=single]
	{s0---failure(true)-->s1, t0---start(true)-->t1},{---:hb_B:13:1-->},   
	(failure(true)=failure(b1:sva_SV0:1:1))
	/\(start(true)=start(b2:sva_SV0:1:1))
	/\(:hb_B:13:1=fail(b0:sva_SV0:1:1))/\((b1:sva_SV0:1:1=b2:sva_SV0:1:1)
	/\(~(b1:sva_SV0:1:1\/b2:sva_SV0:1:1)\/b0:sva_SV0:1:1))
	/\(_fail_=:ra:1:1),{t := Max}
OT ---------------------------------------------------------------------------
		<s0_t0>-----:ra:1:1----><s1_t1>

	{s0---resume(false)-->s0, t0---resume(false)-->t0},{---:hb_B:16:2-->},   
	(resume(false)=resume(b1:sva_SV1:1:2))
	/\(resume(false)=resume(b2:sva_SV1:1:2))
	/\(:hb_B:16:2=resume(b0:sva_SV1:1:2))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2)
	/\(~(b1:sva_SV1:1:2\/b2:sva_SV1:1:2)\/b0:sva_SV1:1:2)
	/\(_resume_=:ra:1:2),{}
OT ---------------------------------------------------------------------------
	<s0_t0>-----:ra:1:2----><s0_t0>

	{},{---:hb_B:118:6-->},(:hb_B:118:6=finish)/\(finish=:ra:1:6),{}
OT ---------------------------------------------------------------------------
	<s0_t0>-----:ra:1:6----><s0_t0>

	{s1---failure(false)-->s1, t1---start(false)-->t1},{---:hb_B:13:1-->},   
	(failure(false)=failure(b1:sva_SV0:1:1))
	/\(start(false)=start(b2:sva_SV0:1:1))
	/\(:hb_B:13:1=fail(b0:sva_SV0:1:1))/\((b1:sva_SV0:1:1=b2:sva_SV0:1:1)
	/\(~(b1:sva_SV0:1:1\/b2:sva_SV0:1:1)\/b0:sva_SV0:1:1))
	/\(_fail_=:ra:1:1),{}
OT ---------------------------------------------------------------------------
	<s1_t1>-----:ra:1:1----><s1_t1>

	{s1---resume(true)-->s0, t1---resume(true)-->t0},{---:hb_B:16:2-->},   
	(resume(true)=resume(b1:sva_SV1:1:2))
	/\(resume(true)=resume(b2:sva_SV1:1:2))
	/\(:hb_B:16:2=resume(b0:sva_SV1:1:2))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2)
	/\(~(b1:sva_SV1:1:2\/b2:sva_SV1:1:2)\/b0:sva_SV1:1:2))
	/\(_resume_=:ra:1:2),{}
OT ---------------------------------------------------------------------------
	<s1_t1>-----:ra:1:2----><s0_t0>

	{t1---tick-->t1},{},(t>0)/\(tick=:ra:1:3),{t := (t-1)}
OT ---------------------------------------------------------------------------
	<s1_t1>-----:ra:1:3----><s1_t1>

	{},{---:hb_B:118:6-->},(:hb_B:118:6=finish)/\(finish=:ra:1:6),{}
OT ---------------------------------------------------------------------------
	<s1_t1>-----:ra:1:6----><s1_t1>

	{s1---timeout-->s2, t1---timeout-->t0}, {},(t=0)/\(ask=:ra:1:4),{}
OT ---------------------------------------------------------------------------
	<s1_t1>-----:ra:1:4----><s2_t0>

	{s2---resume(false)-->s2, t0---resume(false)-->t0},{---:hb_B:16:2-->},   
	(resume(false)=resume(b1:sva_SV1:1:2))
	/\(resume(false)=resume(b2:sva_SV1:1:2))
	/\(:hb_B:16:2=resume(b0:sva_SV1:1:2))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2)
	/\(~(b1:sva_SV1:1:2\/b2:sva_SV1:1:2)\/b0:sva_SV1:1:2))
	/\(_resume_=:ra:1:2),{}
OT ---------------------------------------------------------------------------
	<s2_t0>-----:ra:1:2----><s2_t0>

	{s2---reset-->s0},{},(reset=:ra:1:5),{}
OT ---------------------------------------------------------------------------
	<s2_t0>-----:ra:1:5----><s0_t0>

	{},{---:hb_B:118:6-->},(:hb_B:118:6=finish)/\(finish=:ra:1:6),{}
OT ---------------------------------------------------------------------------
	<s2_t0>-----:ra:1:6----><s2_t0>
\end{lstlisting}

\begin{figure}[h]  
$\begin{array}{r@{}l}
    ot_1  = &\openrule{\{s0 \xrightarrow{\OTvar{fail(true)}} s1, t0 \xrightarrow{\OTvar{start(true)}} t1\}, ~~\{\xrightarrow{hb_1}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
    \OTland \OTvar{start(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland hb_1=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\OTland v_1=\OTvar{\underline{fail}}\OTland \OTvar{b}_1 = \OTvar{b}_2
    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{t := Max\}}
    	   {\ostate{s0,t0} \xrightarrow{v_1} \ostate{s1,t1}}\\
\end{array}$

$\begin{array}{r@{}l}
    ot_2  = &\openrule{\{s0 \xrightarrow{\OTvar{resume(false)}} s0, t0 \xrightarrow{\OTvar{resume(false)}} t0\}, ~~\{\xrightarrow{hb_2}\},~~\OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_1\OTvar{)}\\
    \OTland \OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_2=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\OTland v_2=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
    	    {\ostate{s0,t0} \xrightarrow{v_2} \ostate{s0,t0}}\\
\end{array}$

@@

$\begin{array}{r@{}l}
    ot_6  = &\openrule{\{t1 \xrightarrow{\OTvar{tick}} t1\}, ~~\{\},~~t\neq 0\OTland v_6=\OTvar{tick}, ~~\{t := t-1 \}}
    	   {\ostate{s1,t1} \xrightarrow{v_6} \ostate{s1,t0}}\\
\end{array}$
